The effects of transitions of power on the contents of municipal government websites

### 2017-12-18 paper/presentation/Markus_SPSA_2018_Presentation.tex
presentation

\documentclass[12pt]{beamer}
\setbeamertemplate{navigation symbols}{}
%\usepackage[latin1]{inputenc}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{graphicx}
%\usepackage{draftwatermark}
\usepackage{tikz}
\usepackage{subfigure}
\usetheme{Amsterdam}
\usecolortheme{default}
\title[]{The effects of transitions of power on the contents of
	municipal government websites}
\author{Markus Neumann \\ Bruce Desmarais \\ Hanna Wallach \\ Fridolin Linder}
\institute{The Pennsylvania State University}
\date{January 6, 2018}

\makeatletter
\defbeamertemplate*{footline}{myminiframes theme}
{%
	\begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
	\end{beamercolorbox}
	\hbox{%
		\begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertframenumber/\inserttotalframenumber}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.75\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			\leavevmode{\usebeamerfont{title in head/foot}\insertshorttitle}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}\insertshortauthor}
		\end{beamercolorbox}%
	}%
	\begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
	\end{beamercolorbox}
}
\makeatother

@@

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
	\item Transparency
	\end{itemize}
	}
\end{frame}

\section{Data Collection}
\begin{frame}{wget}
\end{frame}

@@

\begin{frame}{Document filetype \& conversion}
\begin{itemize}
	\item Websites contain a number of different filetypes
	\item txt, pdf, html, doc and docx are useable
	\item convert everything to txt
	\item the file ENDING does not always 
\end{itemize}
\end{frame}

\begin{frame}{Duplicate Line Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Duplicate Line Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Duplicate Line Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\begin{itemize}
		\item Boilerplate
		\item Website elements
	\end{itemize}
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Hash tables for computational efficiency
\end{itemize}
\end{frame}

\begin{frame}{Other preprocessing}
\begin{itemize}
	\item Remove:
	\begin{itemize}
		\item Dates
		\item Numbers
		\item Punctuation
		\item Words not recognized by an English dictionary
		\item Stopwords
		\item Documents with too few unique words
	\end{itemize}
\item Set to lowercase
\item Lemmatization
\end{itemize}
\end{frame}

\section{Analysis}
\begin{frame}{Hierarchical Clustering}
\end{frame}

@@

\begin{frame}{Latent Dirichlet Allocation}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
\end{frame}

>>>>

\documentclass[12pt]{beamer}
\setbeamertemplate{navigation symbols}{}
%\usepackage[latin1]{inputenc}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{graphicx}
%\usepackage{draftwatermark}
\usepackage{tikz}
\usepackage{subfigure}
%\usetheme{Amsterdam}
\usecolortheme{default}
\title[]{The effects of transitions of power on the contents of
	municipal government websites}
\author{Markus Neumann \\ Fridolin Linder \\ Bruce Desmarais}
\institute{The Pennsylvania State University}
\date{January 6, 2018}

\makeatletter
\defbeamertemplate*{footline}{myminiframes theme}
{%
	\begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
	\end{beamercolorbox}
	\hbox{%
		\begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertframenumber/\inserttotalframenumber}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.75\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			\leavevmode{\usebeamerfont{title in head/foot}\insertshorttitle}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertshortauthor}
		\end{beamercolorbox}%
	}%
	\begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
	\end{beamercolorbox}
}
\makeatother

@@

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Content of government websites is an important source of information \& transparency
		\item After coming into power, the Trump administration  has made some controversial changes to the websites of federal agencies
		\item Website content is political
		\item Partisanship of city government is expected to have an effect
	\end{itemize}

}
\end{frame}

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Most local (i.e. mayoral) elections are non-partisan
		\item Few states have exclusively partisan local elections
		\item Data for these elections can be difficult to find
		\item We selected Indiana and Louisiana
	\end{itemize}

	}
\end{frame}

\begin{frame}{Maps}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
\end{figure}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Duplicate content removal
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{The Pipeline}
\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item \textbf{Duplicate content removal}
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

@@

%\begin{frame}{Document filetype \& conversion}
%\begin{itemize}
%	\item Websites contain a number of different filetypes
%	\item txt, pdf, html, doc and docx are useable
%	\item convert everything to txt
%	\item the file ENDING does not always 
%\end{itemize}
%\end{frame}

\begin{frame}{Duplicate Content Removal}
\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\begin{itemize}
		\item Boilerplate
		\item Website elements
	\end{itemize}
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Hash tables for computational efficiency
\end{itemize}
\end{frame}

\begin{frame}{The Pipeline}
\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Duplicate content removal
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

%\begin{frame}{Other preprocessing}
%\begin{itemize}
%	\item Remove:
%	\begin{itemize}
%		\item Dates
%		\item Numbers
%		\item Punctuation
%		\item Words not recognized by an English dictionary
%		\item Stopwords
%		\item Documents with too few unique words
%	\end{itemize}
%\item Set to lowercase
%\item Lemmatization
%\end{itemize}
%\end{frame}

\section{Analysis}
\begin{frame}{Hierarchical Clustering}
\centering
\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
\end{frame}

@@

\begin{frame}{Latent Dirichlet Allocation}

\input{partisanTopWords.tex}

\end{frame}

\begin{frame}{Structural Topic Model}
\input{stmTopWordsINDem.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

\begin{frame}{Structural Topic Model}
\input{stmTopWordsINRep.tex} %../tables/stmTopWordsINRep.tex
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
%\linespread{1.5}
\large
\begin{itemize}
	\item Hierarchical clustering only creates 'topics' if content is VERY similar
	\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
	\item LDA is sensitive to preprocessing, but the most flexible
	\item STM works too, but also very sensitive to duplicate content
	\vspace{5mm}
	\item Democrats focus on raising and spending money, Republicans on infrastructure and basic utilities
\end{itemize}
\end{frame}
